Modeling of Combined Lead Fast Reactor and Concentrating Solar Power Supercritical Carbon Dioxide Cycles to Demonstrate Feasibility, Efficiency Gains, and Cost Reductions

### 2021-11-10 papers/sustainability-1425053/sustainability-1425053-english.tex
Add files via upload
Re-sized Fig. 4 (correct at 2nd attempt)
Add files via upload
Corrected the utter carnage previous change of figure did to the LaTeX so now it looks OK

% \end{paracol}
\begin{figure}[H] 
    %[!h] 
   \widefigure
    \includegraphics[width=\linewidth]{Definitions/c-lfr-on.pdf}
    \caption{Diagram for C-LFR-ON with focus on electricity~generation\label{c-lfr-on}}
\end{figure}
% \begin{paracol}{2}
% %\linenumbers
% \switchcolumn

@@

\noindent 
\begin{tabular}{@{}ll}
\textbf{Variables [Units]}\\
$CR$ & Capacitance ratio [-]\\
$\dot{C}$ & Capacitance rate [MW/$~^{\circ}$C]\\
$\Delta$ & Temperature difference [$~^{\circ}$C]\\
$\delta$ & Approach temperature of heat exchanger [$~^{\circ}$C]\\
$\varepsilon$ & Effectiveness of heat exchanger [-]\\
$\eta$ & Isentropic efficiency [-]\\
$h$ & Enthalpy [J/kg]\\
$\dot{m}$ & Mass flow rate [kg/s]\\
$NTU$ & Number of transfer units [-]\\
$P$ & Pressure [MPa]\\
$\dot{Q}$ & Heat transfer rate [W]\\
$T$ & Temperature []$~^{\circ}$C]\\
$UA$ & Conductivity of heat exchanger [MW/$~^{\circ}$C]\\
$v$ & Volumetric flow rate [$m^3$/kg]\\
$\dot{W}$ & Power [MW]\\
$y$ & Splitter fraction [-]\\
\end{tabular}%
}

>>>>

 \end{paracol}
\begin{figure}[H] 
    %[!h] 
  % \widefigure
    \includegraphics[width=\linewidth]{Definitions/c-lfr-on.pdf}
    \caption{Diagram for C-LFR-ON with focus on electricity~generation\label{c-lfr-on}}
\end{figure}
 \begin{paracol}{2}
% %\linenumbers
 \switchcolumn

@@

\noindent 
\begin{tabular}{@{}ll}
\textbf{Variables [Units]}\\
$CR$ & Capacitance ratio [-]\\
$\dot{C}$ & Capacitance rate [MW/$~^{\circ}$C]\\
$\Delta$ & Temperature difference [$~^{\circ}$C]\\
$\delta$ & Approach temperature of heat exchanger [$~^{\circ}$C]\\
$\varepsilon$ & Effectiveness of heat exchanger [-]\\
$\eta$ & Isentropic efficiency [-]\\
$h$ & Enthalpy [J/kg]\\
$\dot{m}$ & Mass flow rate [kg/s]\\
$NTU$ & Number of transfer units [-]\\
$P$ & Pressure [MPa]\\
$\dot{Q}$ & Heat transfer rate [W]\\
$T$ & Temperature [$~^{\circ}$C]\\
$UA$ & Conductivity of heat exchanger [MW/$~^{\circ}$C]\\
$v$ & Volumetric flow rate [$m^3$/kg]\\
$\dot{W}$ & Power [MW]\\
$y$ & Splitter fraction [-]\\
\end{tabular}%
}
